Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
yu
Update Draft.Rmd

# Create standardize train data for kNN and PCA
# Omit value and id variables since these should not be scaled
train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
#%>% cbind(state=train$state,county=train$county,city=train$city)

@@

```{r kNN}
set.seed(123)
# Find ideal k neighbors
sqrt(nrow(train))

>>>>

# Create standardize train data for kNN and PCA
# Omit value and id variables since these should not be scaled
train_scaled = train %>% select(-id) %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)

@@

```{r kNN uses scaled training data - ALL MODELS FAILED}
set.seed(123)
# Find ideal k neighbors
sqrt(nrow(train))
